Children’s Vocabulary Development in American Sign Language

### 2023-04-19 outputs/paper/paper.qmd
added model to quarto

prod_vocab_model |>
  ggplot(aes(x = age_in_months, y = prod_words)) +
  geom_point(alpha = 0.5) +
  geom_smooth(
    method = "lm",
    se = TRUE,
    color = "black",
    linetype = "dashed",
    formula = "y ~ x"
  ) +
  labs(
    x = "Age (Months)",
    y = "Number of ASL Words Produced"
  ) +
  theme_classic()
```

>>>>

prod_vocab_model |>
  ggplot(aes(x = age_in_months, y = prod_words)) +
  geom_point(alpha = 0.5) +
  geom_smooth(
    method = "lm",
    se = TRUE,
    color = "black",
    linetype = "dashed",
    formula = "y ~ x"
  ) +
  labs(
    x = "Age (Months)",
    y = "Number of ASL Words Produced"
  ) +
  theme_classic()
